A Multiresolution Framework for One Dimensional Neural Field Modelling

### 2011-02-27 Multiresolution_framework/ltx/manuscript.tex
minor edits

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Dynamic spatio-temporal modelling, Expectation Maximisation (EM) algorithm, Integro-Difference Equation (IDE), Multiresolution Approximation (MRA), wavelets.
\end{IEEEkeywords}

@@

The state-space representation of the IDE defined by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} has a $\mathcal Q\left(\boldsymbol\theta,\boldsymbol \theta'\right)$ in a form of

>>>>

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Neural field model, Expectation Maximisation (EM) algorithm, Multiresolution Approximation (MRA), wavelets.
\end{IEEEkeywords}

@@

The state-space representation of the IDE defined by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation} has a quadratic $\mathcal Q\left(\boldsymbol\theta,\boldsymbol \theta'\right)$ in a form of
